Formal Paper Draft

### 2022-01-12 PaperDraft.Rmd
adding updates to the paper doc

Correcting p-values for multiple testing may or may not be necessary depending on how the p-values are intended to be used, although we recommend using Benjamini-Hochberg False Discovery Rate over more conservative Bonferroni corrections (or something similar, assuming that the results are based on p-values as in the Bonferroni Outlier test (Cook & Weisberg, 1982)). We would expect that if the maps are suitably distorted, or *influenced* by a single point, the resulting p-value for the jth PERMANOVA test would be small if the sample sizes are large enough, and quite often will be the smallest p-value generated.

@@

The p-values can instead be construed as providing a sorting of the observations based on their relative extreme-ness.  It stands to reason that, much in the way that Cook's Distance uses F-statistics to identify abberant observations, the pseudo-F statistic or sorted p-value can be compared based solely on relative magnitude. In a setting where only a single influential point is present, we would expect to see that influential point have the smallest p-value (or, equivalently, the largest pseudo-F statistic) of those obtained.

>>>>

@@

We recommend using Benjamini-Hochberg False Discovery Rate (or something similar, assuming that the results are based on p-values as in the Bonferroni Outlier test (Cook & Weisberg, 1982)).  A more conservative approach, such as a Bonferroni correction, would require a significance level to be divided by the number of simultaneous tests performed, $N$, meaning that a Bonferroni-based approach would yield a significance threshold of $\alpha^* = \frac{\alpha}{N}$ which is at least as small as the smallest p-value that is possible to obtain.

Instead, it may make more sense to use the p-values based on their rank regardless of their statistical significance. The p-values can instead be construed as providing a sorting of the observations based on their relative extreme-ness.  It stands to reason that, much in the way that Cook's Distance uses F-statistics to identify abberant observations, the pseudo-F statistic or sorted p-value can be compared based solely on relative magnitude. In a setting where only a single influential point is present, we would expect to see that influential point have the smallest p-value (or, equivalently, the largest pseudo-F statistic) of those obtained.
